\chapter{Conclusions and Recommendations}
\label{chp:10}
\epigraph{I have no special talents. I am only passionately curious.}{Albert Einstein}



\section{Conclusions}

\subsection{Main contributions}

Main thesis contributions are as follows:

\begin{itemize}
    \item Development of a hybrid algorithm with MPCA and HJ, in a multi-stage approach where MPCA performs the exploration and the HJ performs the exploitation.
    \item Development of a hybrid algorithm with $q$G and HJ, in a multi-stage approach where MPCA performs the exploration and the HJ performs the exploitation.
    \item Improvements were made to the MPCA, such as:
    \begin{itemize}[topsep=1em]
        \item hybridization with mechanism derived from Opposition-based Optimization, improving the exploration of the MPCA.
        \item a new Exploitation function was implemented, on a single random dimension at time.
        \item a new scattering probability was tested.
    \end{itemize}
    \item Application of the hybrid algorithms to the damage identification on structures with different complexities implemented in FORTRAN.
    \item Application of the hybrid algorithms to the damage identification on structures with different complexities implemented in NASTRAN.
\end{itemize}

\section{Recommendations}

An itemized list of recommendations are provided below:

\begin{itemize}
    \item Use structures with a higher degrees of freedom than those that were tested in this thesis
    \item
    \item Application
\end{itemize}